---
title: "Resondex Impact Framework"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Resondex Impact Framework}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina = 2
)
```

# Resondex Impact Framework

The **Resondex Impact Framework** is an executive-ready method for ranking business drivers using two complementary dimensions:

- **Impact Magnitude** — Probability Lift (business-interpretable effect size)  
- **Evidence Strength** — Mutual Information (MI) significance (statistical credibility)

This framework ensures prioritization focuses on drivers that are **material in business impact** and **reliable in statistical signal**.

---

## Methodology

### 1) Impact Magnitude — Probability Lift

Resondex defines effect size in probability terms:

> **Probability Lift = P(Outcome | Driver = High) − P(Outcome | Driver = Low)**

This expresses impact in **percentage-point change**, aligning directly with conversion lift, revenue upside, risk change, or behavioral movement.

---

### 2) Evidence Strength — Mutual Information Significance

Resondex evaluates dependency between each driver and the outcome using **Mutual Information (MI)**, which:

- Detects **linear and non-linear relationships**
- Supports **categorical and continuous variables**
- Captures **any meaningful form of dependence**

The associated **MI p-value** reflects the **statistical credibility** of the relationship.

---

### 3) Prioritization Logic — Impact × Evidence

Drivers are categorized using a two-axis evaluation:

- **High Impact + High Evidence** → primary strategic levers (scale and invest)  
- **High Impact + Lower Evidence** → promising opportunities (validate via testing)  
- **Low Impact + High Evidence** → reliable but minor effects (incremental optimization)  
- **Low Impact + Low Evidence** → de-prioritized signals  

---

## Optional: Resondex Impact Score

For dashboard ranking:

- **Impact Score** = `abs(Probability Lift)`  
- **Evidence Score** = `-log10(p_value)`  
- **Resondex Impact Score** = `Impact Score × Evidence Score`

Used for ranking only — underlying metrics should remain visible for transparency.

---

## Client-Ready Half Pager

**Resondex measures each driver two ways.**  
First, we measure **Impact** using **Probability Lift** — the percentage-point change in outcome likelihood when a driver moves from low to high.

Second, we measure **Confidence** using **Mutual Information significance**, which detects both linear and non-linear relationships across categorical and continuous data.

By combining **Impact (magnitude)** and **Confidence (evidence)**, Resondex prioritizes drivers that are both **material in effect** and **statistically credible**, producing a defensible focus list for investment.

---

## Executive One-Pager

### Purpose  
Deliver a ranked, decision-ready view of business drivers balancing **business materiality** with **statistical credibility**.

### How We Measure Impact  
**Impact Magnitude (Probability Lift)**  
Probability Lift = P(Outcome | Driver = High) − P(Outcome | Driver = Low)

**Evidence Strength (Mutual Information Significance)**  
Mutual Information detects any meaningful dependency; MI p-values indicate reliability.

### How We Prioritize  
- High Impact + High Evidence → Scale  
- High Impact + Lower Evidence → Test  
- Low Impact + High Evidence → Optimize  
- Low Impact + Low Evidence → Ignore  

### Outcome  
A ranked list answering:
- What moves outcomes most  
- Which effects we trust  
- Where investment generates the greatest ROI  

---

## Board-Level Bullets

- Measures impact as **probability lift** (business interpretable)  
- Validates reliability using **MI significance**  
- Prioritizes drivers via **Impact × Evidence**  
- Produces a defensible executive ranking  

---

## Example Usage (Optional)

```{r eval=FALSE}
out <- bn_impact(
  obj = bn_fit,
  df = iris,
  dv = "Species",
  ivs = c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width"),
  type = "mi",
  process_subgroups = FALSE,
  n_boot = 10,
  n_querry = 1e4,
  seed = 1
)

out
```

---

## Reporting Language Guidance

Recommended:
- "statistically reliable association"
- "strong evidence of a relationship"

Avoid causal language unless causal methods are used.

---

## Implementation Notes

- Probability Lift emphasizes **interpretability**
- MI p-values reflect **evidence strength**, not causality
- Consider multiple-testing control when evaluating many drivers
